The Schaefer model is typically stated as discussed in Chapter (\ref{ptChapter})
\begin{equation}
\frac{dB}{dt} = r B \left(1-\frac{B}{K}\right) - FB. \label{sheaferOG}
\end{equation}
However under model \ref{schnuteSimple}, when $\gamma=1$, 
$P_s(B;[\alpha, \beta, 1])$ reduces to quadratic logistic production and 
draws a parallel to the logistic production of the typical Schaefer model. 
%discussed in Chapter (\ref{ptChapter}). The typical formulation, and interpretation, of 
The typical Schaefer model does not explicitly include $M$, but rather natural 
mortality is assumed to be implicite in the quadratic form of surplus production. 
That said, if natural mortality is explicitly included in a model with logistic 
production, as seen in Chapter (\ref{schnuteChapter}) under the Schnute model 
when $\gamma=1$, it is straight forward to show that the result is in fact a 
Schaefer model with updated parameters that explicitly model $M$. 
\begin{align}
\frac{dB}{dt} &= \alpha B \left(1-\beta B\right) - (M+F)B \nonumber\\%. \label{sheaferSchnute}
&= \alpha B -\alpha\beta B^2 - M B - F B \nonumber\\
&= (\alpha-M)B -\alpha\beta B^2 - F B \nonumber\\
&= (\alpha-M)B \left(1 - \frac{\alpha\beta}{\alpha-M}B\right) - F B
\end{align}
%Due to the quadratic form of the Schaefer model 
The linear $MB$ term naturally combines with the quadratic form of 
$P_s(B;[\alpha, \beta, 1])$ to simplify into another quadratic 
form that is now directly analogous with the typical Schaefer model seen in 
Eq. (\ref{sheaferOG}). This process produces a Schaefer model with 
the following updated parameters
\begin{align}
\frac{dB}{dt} &= r' B \left(1-\frac{B}{K'}\right) - FB\\
r'=\alpha&-M ~~~~~~~~~ K'=\left(\frac{\alpha-M}{\alpha}\right)\frac{1}{\beta}.
\end{align}
%
%If instead one were to start in the reverse direction, starting with the 
%typical Schaefer model (with implicte natural mortality) and required
%  
%The maximum rate of surplus biomass production, $r'$,  is the difference between the 
%maximum rate of production, $\alpha$, and $M$ 

%A bit of interpretation. Quadratic production of biomass before Mortality.
$P_s(B;[\alpha, \beta, 1])$ represents the biomass production independent of 
mortality. By combining $MB$ into the quadratic form, a new intrinsic 
population growth rate, $r'$, is derived which represents the maximum rate of 
biomass production less natural mortality. %as a net rate of maximum surplus production. 
Similarly, 
%Maximum rate of production is shrunk by $M$.
carrying capacity is shrunk by the factor $\frac{\alpha-M}{\alpha}$ 
which can be interpreted as the percent decrease of $\alpha$ by removing $M$.
% represents as fraction $\alpha$.
% of the maximum rate of biomass production that decreased by $M$.
%maximum rate of surplus biomass production in maximum production by $M$.

%
Furthermore working with $\gamma=1$ in the analytical expression of Schnute RPs, 
as given in Chapter (\ref{schnuteChapter}), analytical RPs take the expected 
values. For example, working with the equation for $\alpha$ from Eq. (\ref{abgSys}), 
with $\gamma=1$, $F^*$ is shown to takes the expected form for a Schaefer model.
\begin{align}
\alpha &= (M+F^*)\left(1+\frac{F^*}{M+F^*}\right) \nonumber\\
       &= M+2F^* \nonumber\\
   F^* &= \frac{\alpha-M}{2} = \frac{r'}{2} 
\end{align}
%By working with Eq (\ref{BsEq}, \ref{B0S}).
Working with Eq. (\ref{B0S}) from the text gives the expected carrying capacity.
\begin{align}
B_0 &= \frac{1}{\beta} \left( 1-\frac{M}{\alpha} \right) \nonumber\\
    &= \frac{\alpha-M}{\alpha\beta} = K'
\end{align}
Furthermore, Eq. (\ref{B0S}) for $B^*$ gives,

\begin{align}
    B^* &= \frac{1}{\beta} \left( 1-\frac{M+\frac{\alpha-M}{2}}{\alpha}\right) \nonumber\\
        &= \frac{1}{\beta} - \frac{M+\alpha}{2\beta\alpha}\nonumber\\
        &= \frac{\alpha-M}{2\alpha\beta} = \frac{K'}{2}.
\end{align}
%
Finally $\frac{B_{MSY}}{B_0}$ in the case of explicite motality is indeed also $\frac{1}{2}$,

%\vspace*{-0.5cm}
\begin{align}
\frac{B^*}{B_0}&=\frac{K'/2}{K'}=\frac{1}{2}.
\end{align}
%\vspace*{-0.25cm}

%
This is a similar model as presented by Aalto et. al. \cite{aalto_separating_2015}, 
albeit their model includes additional dynamics. In terms of the complexity of 
dynamics the model presented by Aalto et. al. is intermediate to the SPMs 
presented in Chapter (\ref{schnuteChapter}) and the DDMs presented in 
Chapter (\ref{delayChapter}). Similar results may be obtained in the DDM 
setting here, although with an explicite handling of numbers and individual 
growth.  
